Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Generalizing code to make easier to change averages or number of individuals

```{r}
mycols <- c("black", "blue", "purple")
#create density plots
curve(dlnorm(x, meanlog=1, sdlog=.3), from=0, to=10, col=mycols[1],
      main = 'Log Normally distributed movement rates for three populations', #add title
      ylab = 'Density', #change y-axis label
      )
curve(dlnorm(x, meanlog=1, sdlog=.5), from=0, to=10, col=mycols[2], add=TRUE)
curve(dlnorm(x, meanlog=1, sdlog=1), from=0, to=10, col=mycols[3], add=TRUE)

@@

```{r}
m_1 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 0.3),3))
m_2 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 0.5),3))
m_3 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 1),3))
```

@@

range <- c(-0.1,15)
#create density plots
curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
      from=range[1], to=range[2], 
      col=mycols[1],
      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
      ylab = 'Density', #change y-axis label
      )
for(i in 2:5){
  curve(dexp(x, 1/m_1[i]), 
        from=range[1], to=range[2],
        col=mycols[i], add=TRUE)
}

@@

```{r}
t <- 100 # Number of time steps
individual <- 5

@@

for(j in 1:individual){
  for(k in 1:10){
  a <- sim_movement(m_1[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
    mutate(indiv = as.factor(j),
           run = paste("r_", k))
  df <- rbind.data.frame(df, a)
}
}

>>>>

av.mov.rate <- 2
max.x <- 20

mycols <- c("black", "blue", "purple")
#create density plots
curve(dlnorm(x, meanlog=av.mov.rate, sdlog=.3),
      from=0, to=max.x,
      col=mycols[1],
      main = 'Log Normally distributed movement rates for three populations', #add title
      ylab = 'Density', #change y-axis label
      )

curve(dlnorm(x, meanlog=av.mov.rate, sdlog=.5), 
      from=0, to=max.x,
      col=mycols[2], add=TRUE)

curve(dlnorm(x, meanlog=av.mov.rate, sdlog=1), 
      from=0, to=max.x,
      col=mycols[3], add=TRUE)

@@

```{r}
n.individuals <- 5
m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 0.3),3))
m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 0.5),3))
m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 1),3))
```

@@

range <- c(-0.1,max.x+5)
#create density plots
curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
      from=range[1], to=range[2], 
      col=mycols[1],
      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
      ylab = 'Density', #change y-axis label
      )
for(i in 2:5){
  curve(dexp(x, 1/m_1[i]), 
        from=range[1], to=range[2],
        col=mycols[i], add=TRUE)
}

@@

```{r eval=FALSE}
t <- 100 # Number of time steps
individual <- 5

@@

for(j in 1:n.individuals){
  for(k in 1:3){
  a <- sim_movement(m_1[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
    mutate(indiv = as.factor(j),
           run = paste("r_", k))
  df <- rbind.data.frame(df, a)
}
}
